### 2022-07-26 manuscript/manuscript.Rmd
prep for publication

---
title             : "A cross-disciplinary assessment of post-publication peer review policies and practice at influential scientific journals."
shorttitle        : "Post-publication peer review"

author:
  - name: 'Tom E. Hardwicke'
    affiliation: '1'
    corresponding: yes
    email: 'tom.hardwicke@uva.nl'
    address: 'Department of Psychology, University of Amsterdam, Nieuwe Achtergracht 129-B, 1018 WT Amsterdam'
  - name: 'Robert T. Thibault'
    affiliation: '2,8'
  - name: 'Jessica E. Kosie'
    affiliation: '4'
  - name: 'Loukia Tzavella'
    affiliation: '7'
  - name: 'Theiss Bendixen'
    affiliation: '3'
  - name: 'Sarah A. Handcock'
    affiliation: '10'
  - name: 'Vivian E. Köneke'
    affiliation: '5'
  - name: 'John P. A. Ioannidis'
    affiliation: '6,9'

@@

abstract: |
  Critical scrutiny of published research is an important feature of a self-correcting scientific ecosystem. Academic journals exert considerable control over criticism submitted in the form of letters, commentaries, or online comments (post-publication peer review, PPPR). Currently, there is limited empirical data documenting how journals handle PPPR. We assessed PPPR policies and practice amongst 330 influential journals operating across 22 scientific disciplines. 123 (37%) journals did not offer any options for submitting PPPR. 207 (63%) journals offered PPPR options, but often imposed limits on length (median 1000, IQR 700 words) and time-to-submit (median 12, IQR 22 weeks). The most restrictive limits were 175 words and 2 weeks; the least restrictive PPPRs had no limits. Of a random sample of 2066 research articles published in 2018 by PPPR-offering journals, we found that 1.9% (95% CI [1.4, 2.6]) were the subject of at least one PPPR. We examined 58 PPPRs and found, for example, that 44 received an author reply, of which 41 asserted that the authors’ conclusions were unchanged. Clinical Medicine stood out as the domain with the most active PPPR culture, with all 15 journals providing PPPR options and publishing the most PPPR, but also imposing the strictest length limits (median 400, IQR 150 words) and time-to-submit limits (median 4, IQR 2 weeks). Overall, our findings suggest that influential academic journals often pose serious barriers to the cultivation, documentation, and dissemination of PPPR. We suggest policies that journals could adopt to promote a richer culture of post-publication critique.

keywords          : "peer review, post-publication peer review, letter to the editor, meta-research, journal policy, self-correction, scientific criticism"

@@

@@

# Introduction
Poor quality research frequently survives peer review and permeates through to the academic literature (Altman, 1994; Hardwicke, Serghiou, et al., 2020; Ioannidis, 2005; Nosek et al., 2021; Van Calster et al., 2021). This highlights the importance of facilitating ongoing critical scrutiny of published research. Post-publication critique can highlight errors, limitations, or alternative interpretations that were not adequately addressed during traditional peer review and help research consumers to make informed judgements about the utility and validity of published scientific claims (Altman, 2005; Bastian, 2014).

Currently, critical discourse about research is fragmented across the scientific ecosystem, ranging from conversations between colleagues, social media exchanges (e.g., blogs, Twitter), and purpose-built online commenting platforms (e.g., PubPeer), to letters or commentaries published in academic journals. These modes of critical discourse have been collectively referred to as ‘post-publication peer review’ (PPPR; Altman, 2002; Bastian, 2014; Winker, 2015). In the present study, we were specifically interested in examining journal-based PPPR (for our operational definition, see Box 1).

Journals may exert considerable control over the cultivation, documentation, and dissemination of PPPR; however, little empirical data is available to systematically evaluate how they handle this important aspect of scientific self-correction. Prior PPPR studies were narrow in scope, mainly limited to medical journals, and now outdated (Altman, 2002; Von Elm et al., 2009; Winker, 2013). The present study sought to provide a systematic, cross-disciplinary, and more contemporary assessment of journal PPPR policies (Study One) and practice (Study Two) amongst 330 highly influential journals operating across 22 scientific disciplines. Our goal is to provide a stratum of empirical evidence to inform debates about how scientific critique should be optimally handled in the scientific ecosystem.

## Box 1. What is post-publication peer review (PPPR)?

PPPR can refer to many forms of critical discourse about published research (Altman, 2002; Bastian, 2014; Winker, 2015). In this study, we focused only on PPPR handled by academic journals according to the following operational definition:

>> Any journal-based avenue for sharing peer-initiated critical discourse related to specific research articles previously published in the same journal.

For scientific discourse to constitute PPPR under this definition, it had to meet the following specific criteria:

(a) Journal-based. The mode of sharing critical discourse had to be directly or indirectly controlled by the journal. Online commenting systems developed by 3rd party services (e.g., Disqus), still counted as PPPR if the journal was responsible for operating them.

(b) Shared. The critique had to be accessible to the journal’s readership, rather than, for example, handled privately within the editorial team. Critical discourse published behind a paywall still counted as PPPR as long as it was visible to the journal’s typical readership.

(c) Peer-initiated. It had to be possible for independent researchers to make unsolicited submissions; commissioned articles and/or editorials did not count as PPPR.

(d) Critical discourse. PPPR had to allow for critical content. Exclusively positive or neutral content (e.g., news or ‘spotlight’ articles) did not count as PPPR.

(e) Related to specific research articles previously published in the journal. The target of PPPR had to be specific research already published in the same journal, rather than research published elsewhere, or articles about general scientific topics or general methodological issues. Systematic reviews and meta-analyses did not count as PPPR.

@@

@@

This was an observational study with a cross-sectional design. We recorded the name and description of any PPPR options offered by journals, limits imposed on PPPR in terms of length (e.g., number of words), time-to-submit (e.g., weeks since publication of the target article), or number of references, and whether PPPRs are sent for independent external peer-review[^1]. We also obtained 2017 Journal Impact Factors and identified whether journals were members of the Committee on Publication Ethics (COPE). For more detail about variables measured in Study One, see Supplementary Information B.

[^1]: We operationally defined 'independent external peer review' as reviews solicited from individuals who were not (a) members of the editorial team or (b) authors of the original article.

The sample consisted of 330 highly influential academic journals operating broadly across science. Specifically, we used Clarivate Journal Citation Reports (https://jcr.clarivate.com) to identify the 15 most highly ranked journals by 2017 Journal Impact Factor in each of 22 high-level scientific domains (defined by Clarivate Essential Science Indicators: https://perma.cc/MD4V-A5X5). We did not include journals that only published reviews. The sample size was chosen based on a precision analysis which is documented in our preregistered protocol (https://osf.io/hjvnw/).

@@

1. Between November, 2019 and January, 2020, we identified and preserved the ‘article types’ section of the author submission guidelines on each journal’s website (Supplementary Information C).

@@

3. Coding was predominantly based on the preserved ‘article types’ documentation to ensure stability and reproducibility (live journal websites can be updated). It was only necessary to examine live journal websites to check for web-based commenting systems. When an ‘article types’ section was not found in step 1, each coder conducted an additional check of the live website and examined the most recently published issue of the journal to see if they could identify any examples of PPPR.

@@

5. If an article type seemed like it might be PPPR, but the description was insufficient to judge, coders checked several published articles of this type to determine whether any met our operational definition of PPPR (Box 1).

6. Because journals used various naming conventions for similar types of PPPR and various units to specify limits (e.g., characters, words, or pages for length limits), we harmonized PPPR names to three types (‘letters [to the editor]’, ‘commentaries’, and ‘web comments’) and transformed units to words (length limits) and weeks (time-to-submit limits). Letters and commentaries were types of articles submitted through the regular manuscript submission system, whereas web comments were submitted via an online interface on the target article webpage. For details, see Supplementary Information D.

@@

Across all 22 scientific fields (n = 330 journals), the median 2017 Journal Impact Factor was `r allFieldChar %>% pull(Median_jif)` (range `r allFieldChar %>% pull(Min_jif)` - `r allFieldChar %>% pull(Max_jif)`) and `r allFieldChar %>% mutate(COPE_report = paste0(COPE_Signatories, ' (', round((COPE_Signatories/330)*100,0),'%)')) %>% pull(COPE_report)` journals were signatories of COPE. Characteristics data for each scientific domain are available in Supplementary Table \@ref(tab:journal-characteristics-table).

### How many journals offer PPPR?

@@

Figure \@ref(fig:fig-policy-freq) shows the number of journals offering any form of PPPR, and different types of PPPR, across 22 scientific domains (for equivalent tabular data, see Supplementary Table F1). Of `r journalsOfferingAnyPPPR$n` journals that offered PPPR, `r pppr_cope` were members of COPE. Of `r journalsOfferingAnyPPPR$N - journalsOfferingAnyPPPR$n` journals that did not offer PPPR, `r no_pppr_cope` were members of COPE.

Journals offering PPPR were most common in `r str_to_title(high_field_PPPR$field)` (n = `r high_field_PPPR$n`, `r high_field_PPPR$percent`%) and least common in `r str_to_title(low_field_PPPR$field)` (n = `r low_field_PPPR$n`, `r low_field_PPPR$percent`%). Overall, `r journalsOfferingOnePPPR` journals offered one PPPR option, `r journalsOfferingTwoPPPR` journals offered two PPPR options, and `r journalsOfferingThreePPPR` journals offered three PPPR options, equating to a total of `r d_policy %>% filter(!is.na(PPPR_name)) %>% nrow()` individual PPPR options across journals.

@@

other_n <- PPPR_names_summary %>% filter(PPPR_name_harmonized == "Other") %>% pull(n)
```
After harmonizing PPPR names, there were `r letters_n` journals offering letters, `r commentaries_n` journals offering commentaries, and `r web_comments_n` journals offering web comments. `r other_n` journals offered other miscellaneous types of PPPR such as ‘Forum papers’ and ‘Update articles’. At least two journals (The British Journal of Psychiatry and The BMJ) offered a hybrid type of PPPR whereby selected web comments (known as ‘eLetters’ and ‘Rapid Responses’ respectively) were chosen by editors to be subsequently (re-)published in the journal print edition as letters. To avoid double counting this data, we classified them only as web comments. There were no cases where multiple PPPR types offered by the same journal were classified with the same harmonized label. A complete list of journals and the PPPR they offered is available in  Supplementary Table G1.

@@

```{r fig-policy-freq, fig.width = 7.5, fig.height = 10, fig.path = 'figs/', fig.cap = 'Number and percentage of journals offering any PPPR options (purple) and the number of specific PPPR options (green) available in all scientific domains (top-left panel) and in each scientific domain (other panels). Note that individual journals can offer multiple PPPR options.'}
megaPlot
```

### What limits did journals place on PPPR?

@@

Table 1 shows how often journal policies imposed limits on PPPR in terms of length, time-to-submit, or number of references. Limits were mostly expressed quantitatively, but sometimes they were qualitative and more ambiguous, for example, stating that PPPR should be ‘concise’ or address ‘recently published’ articles. Often there was no information at all about a particular limit. Occasionally policies explicitly asserted that there was no limit. This happened `r d_policy %>% filter(wordLimits == 'NO') %>% nrow()` time for length limits, `r d_policy %>% filter(timeLimits == 'NO') %>% nrow()` times for time-to-submit limits, and `r d_policy %>% filter(referenceLimits == 'NO') %>% nrow()` times for reference limits. The full distribution of quantitative length limits and time-to-submit limits is displayed in Figure 2 and limits imposed by individual journals are available in Supplementary Table G1. Table 1 also shows whether PPPR was subject to independent external peer review (for details see Supplementary Table H1).

@@

```{r fig-policy-limits, fig.width = 7.5, fig.height = 7.5, fig.path = 'figs/', fig.cap = 'Limits imposed by journals on PPPR in terms of (A) length and (B) time-to-submit PPPR since publication of the target article. A1 and B1 show the number of PPPR options for which the journal did not state if there was a limit (“Not stated”), explicitly stated there was not a limit (“None”), stated a qualitative limit (“Qual”), or stated a quantitative limit (“Quant”). Quantitative limits are displayed in A2 and B2 as a histogram and boxplot with the dark line representing the median, lower and upper hinges representing the 25th and 75th percentiles, and upper and lower whiskers representing the ± 1.5 interquartile range.'}
(wrap_elements(row_one) / wrap_elements(row_two) ) & theme(plot.margin = margin(0, 0, 0, 0, "cm")) 
#p2 / p4
```

@@

```{r pppr-limits-table}
pppr_types_tab %>% kable(col.names = c("PPPR","n","n (%)","n (%)","Md (IQR)","n (%)","n (%)","Md (IQR)","n (%)","n (%)","Md (IQR)","n (%)"), caption = 'PPPR types and their length, time-to-submit, or reference limits. The table shows the number (n) and percentage  of PPPR types that are subject to any (qualitative or quantitative) limit, quantitative limits specifically, and the median (Md) and interquartile range (IQR) for quantitative limits. The table also shows whether the author submission guidelines state that the PPPR types are sent for independent external peer review either routinely or at the editor’s discretion (for details see Supplementary Information H).', booktabs = T) %>% kable_styling(latex_options="scale_down") %>% add_header_above(c(" " = 2, "Length" = 3, "Time-to-submit" = 3, "References" = 3, "Peer review" = 1))
```

Because some journals offered more than one type of PPPR, Figure \@ref(fig:fig-policy-limits)  does not give a complete picture of journal-level limits on PPPR. For example, an individual journal may compensate for a restrictive form of PPPR by also offering a less restrictive form of PPPR. This is difficult to assess systematically across the whole sample because of interactions between different limit types and the ambiguity of qualitative limits. However, in Table 2 we provided a focused examination of the 20 journals that offered the most restrictive PPPR options in terms of quantitative length and time-to-submit limits. To build this table, we created two separate lists of PPPR ranked by quantitative length limits and time limits respectively. We then identified the top ten journals in each ranked list. To handle duplicates within- or between- lists, we retained the higher ranked instance and replaced the lower ranked instance until we had 20 unique journals overall (Table 2).

@@

```{r most-restrictive-table}
d_policy %>% filter(!is.na(PPPR_name), journal %in% restrict_all) %>% 
  select(journal, PPPR_name_harmonized, wordLimits, timeLimits) %>% 
  mutate(
    journal = str_to_title(journal),
    across(c(wordLimits,timeLimits), ~recode(., "NOT STATED" = "Not specified", "Qualitative limit" = "Qual limit"))) %>%
  kable(col.names = c('journal', 'PPPR', 'word limits', 'time limits'), caption = "Twenty journals that offered the most restrictive PPPR options. Journals were selected based on having the most restrictive quantitative length and time-to-submit limits for at least one of their PPPR options. Some of these journals also offered additional less restrictive PPPR options, which we have included and marked with asterisks. When PPPR were subject to qualitative limits, the verbatim policy text is shown. Journals are presented in alphabetical order. Journal of the American Medical Association (JAMA) journals are clustered because they had identical PPPR policies.", booktabs = T, longtable = T) %>% kable_styling(latex_options=c("hold_position", "scaledown")) %>% column_spec(1, width = "15em")
```

From Table 2, it is notable that 8 of the journals offering the most restrictive PPPR options operate in the domain of Clinical Medicine. Overall in this domain, journals specified strict limits on length (19 PPPR policies with a quantitative limit: median 400, IQR 150 words; 3 PPPR policies did not mention a limit) and time-to-submit (13 PPPR policies with a quantitative limit: median 4, IQR 2 weeks; 3 PPPR policies stated a qualitative limit, 5 PPPR policies did not mention a limit, 1 PPPR policy stated there was no limit). Table 2 also suggests that restrictive PPPR options are sometimes accompanied by less restrictive PPPR options. Eleven of the 20 journals only offered one PPPR option. Nine of the 20 journals offered web comments in addition to letters and, in general, web comment policies appeared to be less restrictive than letters. However, this was often unclear because exact quantitative limits were not specified and most differences were marginal. For example, in the JAMA family of journals, letters must be less than 400 words and submitted within 4 weeks of target article publication. By contrast, web comments are marginally less restrictive in terms of length (600 words), and ambiguous about their time-to-submit limits (“We may reject comments because they...are submitted a long time after article publication”). One journal - Science - offered commentaries (called ‘Technical Comments’) in addition to letters and web comments. In this case, letters and commentaries shared a time-to-submit limit of 3 months, and commentaries had a somewhat less restrictive length limit than letters (1000 vs. 300 words). By contrast, no time-to-submit limit was specified for web comments and an ambiguous length limit was implied (web comments should be ‘brief’).

@@

med_journ_limits %>% count(wordLimits)
med_journ_limits %>% count(timeLimits)

med_journ_limits %>% select(wordLimits) %>% filter(wordLimits != "NOT STATED") %>% mutate(wordLimits = as.numeric(wordLimits)) %>% pull(wordLimits) %>% median()
med_journ_limits %>% select(wordLimits) %>% filter(wordLimits != "NOT STATED") %>% mutate(wordLimits = as.numeric(wordLimits)) %>% pull(wordLimits) %>% IQR()
med_journ_limits %>% select(timeLimits) %>% filter(timeLimits %notin% c("NOT STATED", "Qualitative limit", "NO")) %>% mutate(timeLimits = as.numeric(timeLimits)) %>% pull(timeLimits) %>% median()
med_journ_limits %>% select(timeLimits) %>% filter(timeLimits %notin% c("NOT STATED", "Qualitative limit", "NO")) %>% mutate(timeLimits = as.numeric(timeLimits)) %>% pull(timeLimits) %>% IQR()
```

@@

### Design
This was an observational study with a cross-sectional design. The goal of Study Two was to examine PPPR in practice at the 207 journals that offered PPPR according to Study One. We used two measures of PPPR prevalence. Our primary (preregistered) estimate of PPPR prevalence was based on how many of 10 randomly sampled articles per journal were linked to PPPR. As one journal - Wildlife Monographs only published 6 articles in 2018, the total number of assessed articles was 2066. An article was considered linked to PPPR if the article webpage mentioned the existence of relevant PPPR.

After Study One, but before beginning Study Two, we decided to also compute a secondary (not preregistered) PPPR prevalence estimate based on how many of randomly sampled articles were themselves examples of PPPR. To align the two estimates, we only used the first 10 eligible articles for each journal, and therefore the total number of assessed articles was 2066 as above. These two prevalence measures have complementary strengths and limitations. For the primary prevalence estimate PPPR was identified through searches of article web pages for linked PPPR. Its accuracy therefore depends on journals actively and visibly linking to PPPR on their webpages. However, it is not dependent on PPPR being indexed in Web of Science databases. By contrast, for the secondary prevalence estimate PPPR was identified by checking if sampled articles were themselves examples of PPPR. Thus, it does not rely on journals linking to relevant PPPR, but it does rely on PPPR being indexed in Web of Science databases, because that is how the sampled articles were identified. Note that our primary estimate was also time-restricted in the sense that any identified PPPR must have been published after 2018 (when the sampled articles were published). By contrast, our secondary estimate could theoretically detect PPPRs pertaining to any previously target articles, regardless of their publication date.

>>>>

---
title             : "Post-publication critique at top-ranked journals across scientific disciplines: A cross-sectional assessment of policies and practice"
shorttitle        : "Post-publication critique"

author:
  - name: 'Tom E. Hardwicke'
    affiliation: '1'
    corresponding: yes
    email: 'hardwickete@gmail.com'
    address: 'Department of Psychology, University of Amsterdam, Nieuwe Achtergracht 129-B, 1018 WT Amsterdam'
  - name: 'Robert T. Thibault'
    affiliation: '2,8'
  - name: 'Jessica E. Kosie'
    affiliation: '4'
  - name: 'Loukia Tzavella'
    affiliation: '7'
  - name: 'Theiss Bendixen'
    affiliation: '3'
  - name: 'Sarah A. Handcock'
    affiliation: '10'
  - name: 'Vivian E. Köneke'
    affiliation: '5'
  - name: 'John P. A. Ioannidis'
    affiliation: '6,9'

@@

abstract: |
  Journals exert considerable control over letters, commentaries, and online comments that criticize prior research (post-publication critique). We assessed policies (Study One) and practice (Study Two) related to post-publication critique at 15 top-ranked journals in each of 22 scientific disciplines (N=330 journals). 207 (63%) journals accepted post-publication critique and often imposed limits on length (median 1000, interquartile range [IQR] 500-1200 words) and time-to-submit (median 12, IQR 4-26 weeks). The most restrictive limits were 175 words and 2 weeks; some policies imposed no limits. Of 2066 randomly sampled research articles published in 2018 by journals accepting post-publication critique, 39 (1.9%, 95% confidence interval [1.4, 2.6]) were linked to at least one post-publication critique (there were 58 post-publication critiques in total). Of the 58 post-publication critiques, 44 received an author reply, of which 41 asserted that original conclusions were unchanged. Clinical Medicine had the most active culture of post-publication critique: all journals accepted post-publication critique and published the most post-publication critique overall, but also imposed the strictest limits on length (median 400, IQR 400-550 words) and time-to-submit (median 4, IQR 4-6 weeks). Our findings suggest that top-ranked academic journals often pose serious barriers to the cultivation, documentation, and dissemination of post-publication critique.

keywords          : "peer review, post-publication critique, letter to the editor, meta-research, journal policy, self-correction, scientific criticism"

@@

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

@@

# Introduction
Poor quality research frequently survives peer review and permeates through to the academic literature (Altman, 1994; Hardwicke, Serghiou, et al., 2020; Ioannidis, 2005; Nosek et al., 2022; Van Calster et al., 2021). This highlights the importance of ongoing critical scrutiny of published research to identify errors, limitations, or alternative interpretations that were not adequately addressed during pre-publication peer review. Such critiques may help research consumers to make more informed judgements about the utility and validity of published scientific claims (Altman, 2005; Bastian, 2014).

Journals exert considerable control over criticism of prior research submitted in the form of letters, commentaries, or online comments (Altman, 2002; Winker, 2015). We refer to these collectively as ‘post-publication critique’ (see Supplementary Information K for an operational definition). Currently, there is limited empirical data available to systematically evaluate how journals handle this important aspect of scientific self-correction. Prior studies of post-publication critique were narrow in scope, mainly focused on medical journals, and are now outdated (Altman, 2002; Kastner et al., 2013; Von Elm et al., 2009; Winker, 2013). In the present research, we sought to provide a systematic, cross-disciplinary, and more contemporary assessment of journal policies (Study One) and practice (Study Two) related to post-publication critique at 330 top-ranked journals operating in 22 scientific disciplines (Supplementary Information M provides a schematic illustration of the two studies). Our goal was to generate empirical evidence to inform debates about how scientific critique should be optimally handled by academic journals.

@@

The sample consisted of 15 academic journals, top-ranked by 2017 Journal Impact Factor operating in each of 22 scientific disciplines (N = 330 journals). This represents the entire population of interest. Journal Impact Factors were identified using Clarivate Journal Citation Reports (https://jcr.clarivate.com). Scientific disciplines were defined by Clarivate Essential Science Indicators: https://perma.cc/MD4V-A5X5; Supplementary Information L). We did not include journals that only published reviews. The sample size was chosen based on a precision analysis which is documented in our preregistered protocol (https://osf.io/hjvnw/).

@@

The study had a cross-sectional design. The measured variables (see Supplementary Information B for details) were the name and description of any options for post-publication critique offered by each journal (e.g., letters), limits imposed on post-publication critique in terms of length (e.g., number of words), time-to-submit (e.g., weeks since publication of the target article), or number of references, and whether post-publication critiques are sent for independent external peer-review (reviews solicited from individuals who were not members of the editorial team or authors of the target article). We also obtained 2017 Journal Impact Factors and identified whether journals were members of the Committee on Publication Ethics (COPE).

@@

1.	Between November, 2019, and January, 2020, TEH and VEK identified and preserved the ‘article types’ section of the author submission guidelines on each journal’s website (Supplementary Information C).

@@

3.	Coding was predominantly based on the preserved ‘article types’ documentation to ensure stability and reproducibility (live journal websites can be updated). It was only necessary to examine live journal websites to check for web-based commenting systems. When an ‘article types’ section was not found in step 1, each coder conducted an additional check of the live website and examined the most recently published issue of the journal to see if they could identify any examples of post-publication critique.

@@

5.	If an article type seemed like it might be post-publication critique, but the description was insufficient to judge, coders checked several published articles of this type to determine whether any met our operational definition of post-publication critique (Supplementary Information K).

6.	Because journals used various naming conventions for similar types of post-publication critique and various units to specify limits (e.g., characters, words, or pages for length limits), we harmonized names to four types (‘letters [to the editor]’, ‘commentaries’, ‘web comments’, and ‘other’) and transformed units to words (length limits) and weeks (time-to-submit limits). Letters and commentaries were types of articles submitted through the regular manuscript submission system, whereas web comments were submitted via an online interface on the target article webpage. For details, see Supplementary Information D.

@@

Across all 22 scientific disciplines (n = 330 journals), the median 2017 Journal Impact Factor was `r allFieldChar %>% pull(Median_jif)` (range `r allFieldChar %>% pull(Min_jif)` - `r allFieldChar %>% pull(Max_jif)`). `r allFieldChar %>% mutate(COPE_report = paste0(COPE_Signatories, ' (', round((COPE_Signatories/330)*100,0),'%)')) %>% pull(COPE_report)` journals were members of COPE. Characteristics for each scientific discipline are available in Supplementary Table E1.

### How many journals offer post-publication critique?

@@

Figure \@ref(fig:fig-policy-freq) shows the number of journals offering any form of post-publication critique, and specific types of post-publication critique, across 22 scientific disciplines (for equivalent tabular data, see Supplementary Table F1). Of `r journalsOfferingAnyPPPR$n` journals that offered post-publication critique, `r pppr_cope` (`r round(pppr_cope/journalsOfferingAnyPPPR$n,2)*100`%) were members of COPE. Of `r journalsOfferingAnyPPPR$N - journalsOfferingAnyPPPR$n` journals that did not offer post-publication critique, `r no_pppr_cope` (`r round(no_pppr_cope/(journalsOfferingAnyPPPR$N - journalsOfferingAnyPPPR$n),2)*100`%) were members of COPE.

Journals offering post-publication critique were most common in `r str_to_title(high_field_PPPR$field)` (n = `r high_field_PPPR$n`, `r high_field_PPPR$percent`%) and least common in `r str_to_title(low_field_PPPR$field)` (n = `r low_field_PPPR$n`, `r low_field_PPPR$percent`%). Overall, `r journalsOfferingOnePPPR` journals offered one option for post-publication critique, `r journalsOfferingTwoPPPR` journals offered two options, and `r journalsOfferingThreePPPR` journals offered three options, equating to a total of `r d_policy %>% filter(!is.na(PPPR_name)) %>% nrow()` individual post-publication critique options across journals.

@@

other_n <- PPPR_names_summary %>% filter(PPPR_name_harmonized == "Other") %>% pull(n)
```
After post-publication critique names were harmonized into four types, there were `r letters_n` journals offering letters, `r commentaries_n` journals offering commentaries, and `r web_comments_n` journals offering web comments. `r other_n` journals offered other miscellaneous types of post-publication critique such as ‘Forum papers’ and ‘Update articles’. A complete list of journals and their post-publication critique options is available in  Supplementary Table G1.

@@

```{r fig-policy-freq, fig.width = 7.5, fig.height = 10, fig.path = 'figs/', fig.cap = 'Number and percentage of journals offering any (purple) and specific (green) options for post-publication critique (PPC) in all scientific disciplines (top-left panel, n = 330 journals) and in individual scientific disciplines (other panels, n = 15 journals). Note that individual journals can offer multiple post-publication critique options.'}
megaPlot
```

### What limits did journals place on post-publication critique?

@@

Table 1 shows how often journal policies imposed limits on post-publication critique in terms of length, time-to-submit, or number of references. Limits were mostly expressed quantitatively, but sometimes they were qualitative and more ambiguous, for example, stating that post-publication critique should be ‘concise’ or address ‘recently published’ articles. Often there was no information at all about a particular limit. Occasionally policies explicitly asserted that there was no limit. This happened `r d_policy %>% filter(wordLimits == 'NO') %>% nrow()` time for length limits, `r d_policy %>% filter(timeLimits == 'NO') %>% nrow()` times for time-to-submit limits, and `r d_policy %>% filter(referenceLimits == 'NO') %>% nrow()` times for reference limits. The full distribution of quantitative length limits and time-to-submit limits is displayed in Figure 2 and limits imposed by individual journals are available in Supplementary Table G1. Table 1 also shows whether post-publication critique was subject to independent external peer review (for details see Supplementary Table H1).

@@

```{r fig-policy-limits, fig.width = 7.5, fig.height = 7.5, fig.path = 'figs/', fig.cap = 'Limits imposed by journals on post-publication critique (PPC) in terms of (A) length and (B) time-to-submit since publication of the target article. A1 and B1 show the number of post-publication critique options for which the journal did not state if there was a limit (“Not stated”), explicitly stated there was not a limit (“None”), stated a qualitative limit (“Qual”), or stated a quantitative limit (“Quant”). Quantitative limits are displayed in A2 and B2 as a histogram and boxplot with the dark line representing the median, lower and upper hinges representing the 25th and 75th percentiles, and upper and lower whiskers representing the ± 1.5 interquartile range.'}
(wrap_elements(row_one) / wrap_elements(row_two) ) & theme(plot.margin = margin(0, 0, 0, 0, "cm")) 
#p2 / p4
```

@@

```{r pppr-limits-table}
pppr_types_tab %>% kable(col.names = c("PPPR","n","n (%)","n (%)","Md (IQR)","n (%)","n (%)","Md (IQR)","n (%)","n (%)","Md (IQR)","n (%)"), caption = 'Post-publication critique types and their length, time-to-submit, or reference limits. The table shows the number (n) and percentage (\\%) of post-publication critique types that are subject to any (qualitative or quantitative) limit, quantitative limits specifically, and the median (Md) and interquartile range (IQR) for quantitative limits. The table also shows whether the author submission guidelines state that the post-publication critique types are sent for independent external peer review either routinely or at the editor’s discretion (for details see Supplementary Information H).', booktabs = T) %>% kable_styling(latex_options="scale_down") %>% add_header_above(c(" " = 2, "Length" = 3, "Time-to-submit" = 3, "References" = 3, "Peer review" = 1))
```

Because some journals offered more than one type of post-publication critique, Figure \@ref(fig:fig-policy-limits)  does not give a complete picture of journal-level limits. For example, an individual journal may compensate for a restrictive form of post-publication critique by also offering a less restrictive form. This is difficult to assess systematically across the whole sample because of interactions between different limit types and the ambiguity of qualitative limits. However, in Table 2 we provided a focused examination of the 20 journals that offered the most restrictive post-publication critique options in terms of quantitative length and time-to-submit limits. To build this table, we created two separate lists of post-publication critique ranked by quantitative length limits and time limits respectively. We then identified the top ten journals in each ranked list. To handle duplicates within- or between- lists, we retained the higher ranked instance and replaced the lower ranked instance until we had 20 unique journals overall (Table 2).

@@

```{r most-restrictive-table}
d_policy %>% filter(!is.na(PPPR_name), journal %in% restrict_all) %>% 
  select(journal, PPPR_name_harmonized, wordLimits, timeLimits) %>% 
  mutate(
    journal = str_to_title(journal),
    across(c(wordLimits,timeLimits), ~recode(., "NOT STATED" = "Not specified", "Qualitative limit" = "Qual limit"))) %>%
  kable(col.names = c('journal', 'PPPR', 'word limits', 'time limits'), caption = "Twenty journals that offered the most restrictive options for post-publication critique. Journals were selected based on having the most restrictive quantitative length and time-to-submit limits for at least one of their post-publication critique options. Some of these journals also offered additional less restrictive options, which we have included and marked with asterisks. When post-publication critiques were subject to qualitative limits, the verbatim policy text is shown. Journals are presented in alphabetical order. Journal of the American Medical Association (JAMA) journals are clustered because they had identical post-publication critique policies.", booktabs = T, longtable = T) %>% kable_styling(latex_options=c("hold_position")) %>% column_spec(1, width = "15em")
```

From Table 2, it is notable that 8 of the journals offering the most restrictive options for post-publication critique operate in the discipline of Clinical Medicine. Overall, medical journals specified strict limits on length (19 policies with a quantitative limit: median 400, IQR 150 words; 3 policies did not mention a limit) and time-to-submit (13 policies with a quantitative limit: median 4, IQR 2 weeks; 3 policies stated a qualitative limit, 5 policies did not mention a limit, 1 policy stated there was no limit). Table 2 also suggests that restrictive options for post-publication critique are sometimes accompanied by less restrictive options. Eleven of the 20 journals only offered one option for post-publication critique. Nine of the 20 journals offered web comments in addition to letters and, in general, web comment policies appeared to be less restrictive than letters. However, this was often unclear because exact quantitative limits were not specified and most differences were marginal. For example, in the JAMA family of journals, letters must be less than 400 words and submitted within 4 weeks of target article publication. By contrast, web comments are marginally less restrictive in terms of length (600 words), and ambiguous about their time-to-submit limits (“We may reject comments because they...are submitted a long time after article publication”). One journal - Science - offered commentaries (called ‘Technical Comments’) in addition to letters and web comments. In this case, letters and commentaries shared a time-to-submit limit of 3 months, and commentaries had a somewhat less restrictive length limit than letters (1000 vs. 300 words). By contrast, no time-to-submit limit was specified for web comments and an ambiguous length limit was implied (web comments should be ‘brief’).

@@

#med_journ_limits %>% count(wordLimits)
#med_journ_limits %>% count(timeLimits)

#med_journ_limits %>% select(wordLimits) %>% filter(wordLimits != "NOT STATED") %>% mutate(wordLimits = as.numeric(wordLimits)) %>% pull(wordLimits) %>% median()
#med_journ_limits %>% select(wordLimits) %>% filter(wordLimits != "NOT STATED") %>% mutate(wordLimits = as.numeric(wordLimits)) %>% pull(wordLimits) %>% IQR()
#med_journ_limits %>% select(timeLimits) %>% filter(timeLimits %notin% c("NOT STATED", "Qualitative limit", "NO")) %>% mutate(timeLimits = as.numeric(timeLimits)) %>% pull(timeLimits) %>% median()
#med_journ_limits %>% select(timeLimits) %>% filter(timeLimits %notin% c("NOT STATED", "Qualitative limit", "NO")) %>% mutate(timeLimits = as.numeric(timeLimits)) %>% pull(timeLimits) %>% IQR()
```

@@

### Sample
The sample consisted of 10 randomly sampled eligible articles published in 2018 for each of the 207 journals that offered post-publication critique in principle (according to the results of Study One), aside from one journal, Wildlife Monographs, which only published 6 articles in 2018. Thus, the sample size was 2066 articles.

To obtain this sample, one author (TEH) downloaded bibliographic records from Clarivate Web of Science for all articles published in each journal offering post-publication critique in 2018. We did not include records with meta-data indicating that the article was a ‘Correction’, ‘Retraction’, ‘News Item’, ‘Book Review’, ‘Meeting Abstract’, or ‘Biographical-Item’. The remaining records were randomly shuffled using the ‘sample’ function in R. During manual inspection, additional articles were excluded if they (1) could not be found or accessed; (2) were non-English language; (3) had been retracted; or (4) did not include substantive research: specifically, we excluded news, book reviews, editorials, previews, or similar, and included empirical research, case studies, simulations, proofs, theoretical papers, reviews, meta-analyses, and perspectives (if they were predominantly evidence-based rather than opinion-based). If articles were themselves examples of post-publication critique, they were also excluded for the purposes of our primary prevalence measure, but included for the purposes of our secondary prevalence measure.

### Design
The study had a cross-sectional design. The goal of Study Two was to examine post-publication critique in practice at the 207 journals that offered post-publication critique according to Study One. We used two measures of post-publication critique prevalence. Our primary (preregistered) estimate of prevalence was based on how many of 10 randomly sampled articles per journal were linked to post-publication critique. As one journal - Wildlife Monographs only published 6 articles in 2018, the total number of assessed articles was 2066. An article was considered linked to post-publication critique if the article webpage mentioned the existence of relevant post-publication critique.
